A VLT/FORS2 Narrowband Imaging Search for \ion{Mg}{2} Emission Around $\lowercase{z}\sim0.7$ Galaxies

### 2018-01-03 Manuscript/vaught_2017.tex
update tex file

\begin{document}
\title{A VLT/FORS2 Narrowband Imaging Search for MgII Emission Around z$\sim$0.7 Galaxies }
\author{Ryan Rickards Vaught \altaffilmark{1}, Kate Rubin \altaffilmark{1}, Fabrizio Arrigoni Battaia \altaffilmark{2}, Xavier Prochaska, Joseph Hennawi}

@@

\begin{abstract}
Galactic-scale outflows are thought to be the primary mechanism in the removal of cool gas in star-forming galaxies. Presently, the mass and energy of these flows remain poorly constrained. One way to better constrain these parameters is to measure the spatial extent of the outflow; however, measuring the spatial extent of such outflows via spectral methods has been traditionally very difficult due to the faintness of emission lines tracing outflowing material. We present VLT/FORS2 narrowband imaging of 5 star forming galaxies at redshift z=0.67-0.69 in the GOODS-S field as part of an effort to spatially resolve large-scale outflows traced by MgII emission. Previous spectra of this sample have already revealed winds traced by MgII absorption. At our sample redshift, the MgII emission lines fall exactly within the FORS2 HeII+47 and HeII/3000+48 interference filters. The total integration time of 10 hrs obtained in each filter permits the analysis of the flow surface brightness and extent on scales over which MgII is typically detected in absorption ( i.e, projected distances > 100 kpc). Such measurements can provide stronger constraints on the mass and energy of feedback, helping to advance our understanding of the processes regulating galaxy evolution up to z=1. 
\end{abstract}

@@

\section{Introduction}
Galactic scale outflows are considered to be the main driver of galaxy evolution, as they provide a means to transport cool gas away from star forming regions out to the intergalactic medium. In other words, this removal of cool gas carries away the necessary fuel that is required for stellar formation. Even though outflows play a critical role in the star formation rates and mass of a the host galaxy\citep{Werk_2014}, the physical production mechanism that powers these outflows remains uncertain. Despite the uncertainty, some possible mechanics have been proposed by theoretical studies that include thermal pressure from core collapse supernova, radiation pressure from starbursts and finally cosmic ray pressure\citep{Sugahara_2017,Larson_1974,Chevalier_1985,Springel_2003}. An accurate picture of what types of galaxies host outflows comes from numerous spectroscopic studies(authors), as outflows are detected by measuring the blueshift of absorption transitions with respect to the host galaxy systematic velocities. Spectroscopy of galaxies from small to large redshifts and over a wide range of star formation sequence have revealed outflows in galaxies which host a large concentrations of massive stars (e.g., \cite{Rubin_2014} Martin 2012).

One common practice in detecting the presence of gas in distant galaxies has been to spectroscopically probe galactic halos along background quasar sight lines and down-the-barrel observations. With temperatures of the cool halo gas component on the order of $10^4\ K$, the gas can be traced by the absorption of metals such \ion{Mg}{2}, Fe and others \citep{Bordoloi_2011, Bergeron_1986}.  Nonetheless, this method is weak in constraining the overall radial profile, extent and morphology of the outflow. It follows from these weak constraints that estimates of mass and energy loss are left uncertain by at least two order of magnitude \citep{Rubin_2011}.

In a study by \cite{Rubin_2010a} strong \ion{Mg}{2} emission with a P-Cygni line profile was observed in the GOODS-N galaxy TKRS 4389. A proposed production mechanism for the observed \ion{Mg}{2} emission is photon scattering.

\section{Observations and Data Reduction}
Our sample consists of 5 GOODS-S galaxies. These galaxies were selected from a Keck/LRIS survey of UV absorption lines in 100 objects having redshifts $0.3< z , 1.4$ and $B_{AB}< 23$ in fields with deep HST/ACS imaging \cite{Rubin_2014}. The full sample is fortuitously distributed on the sky such that it can be imaged in a single FORS2 pointing.

The data were taken in service-mode using the FORS2 instrument on the VLT 8.2m telescope Antu between October 2012 and February 2013. We used two narrowband filters, HeII+47 and HeII/3000+48, that have peak transmission at wavelengths that correspond to the MgII doublet lines at our sample redshift of $z\approx 0.7$, (see Table \ref{tab:filters}). The FORS2 has a pixel scale of $0.25''$ pixel$^{-1}$ and a field of view of $7'\times7'$. Summing the individual exposure times for each image results in a combined exposure time of $10.0$ hours each for the HeII+47 and HeII/3000+48 filters. We carried out our observations under photometric and thin cloud conditions (program ID: 090.A-0427A).

\begin{figure}[!h]
\centering
\includegraphics[scale=.55]{sample_v2.png}
\caption{HST/ACS imaging of the each galaxy in our sample. From Top Left to Right Bottom: J033230.03, J033230.64, J033225.26, J033231.36, J033230.57.}
\end{figure}

\begin{figure}[h]
\centering
\includegraphics[scale=.55]{avg_seeing_HEII.pdf}
\includegraphics[scale=.55]{avg_seeing_HEII3000.pdf}
\caption{ The seeing conditions were calculated by ESO and were provided in the header of each science image. \textbf{(Top)} Distribution of seeing for the HeII+47 images. The median seeing is $1.03''$ \textbf{(Bottom)} : Same for the HEII/3000+48 images. The median seeing is $1.08''$ }
\end{figure}

The data were reduced using custom routines written in \textbf{Python}. The images were first corrected by subtracting and removing the overscan region of the CCD. Then the images were bias-subtracted and flat-fielded using twilight flats. Each individual image was cleaned of cosmic rays and bad pixels by utilizing the L.A Cosmic algorithm. The astrometry solutions were calculated via Astrometry.net \citep{Lang} with a standard deviation in the galaxy coordinates of $\sigma \approx 0.10''$.

Before image stacking, we ran each frame through \textbf{SExtractor} \citep{Bertin} in order to create a Root-Mean-Square map of each science image. These frames, in addition to the science images, are stacked to create a co-added RMS image.

The final stacked images for each filter is obtained using \textbf{SWarp} \citep{Bertin}. Each individual frame is first sky-subtracted using a background mesh size of 256 pixels which is approximately $64''$. We chose the mesh size to be large enough such that the extended emission is not mistakenly subtracted \citep{Battaia_2015}. The frame, after background-subtraction, is resampled onto a common astrometric solution using a \textit{Lancosz3} interpolation kernel. The images are median-combined in order to increase the signal to noise of any MgII emission. \textbf{SWarp} is also configured to produce RMS weight map from our \textbf{SExtractor} weighted images.

Once image stacking was done, we were left with two images to perform photometry on. One image contains only continuum photons, while the other one contains continuum + MgII photons.  (see Figure \ref{fig:stacked_image}). One side effect from stacking is that the east and west borders of each image contain greater noise compared to the center of the image. This is due to the imperfect overlap of the 3 pointings used. However, the sample galaxies are sufficiently distant from these low S/N regions that their photometry is not affected. As a final step, both images are aligned in physical coordinates via the IRAF \textbf{Imalign} command \citep{Tody_1986}.

@@

\begin{table*}[t]
\centering
\caption{Properties of 5 galaxies in our sample :  These properties were taken from \cite{Rubin_2014}. All galaxies are at roughly the same redshift. The star formation rates for the sample range from 3.8 to 40.5 solar mass per year. The EW are for the blended components of the MgII doublet and were calculated with Eq. \ref{eq:specEW} and the supplemental Keck/LRIS spectra}
\begin{tabular}{lllllll} \hline \hline
Object & R.A. & Dec  & $z$ & SFR($M_{\odot} yr^{-1}$) & $\log{M_{*}/M_{\odot}}$ & EW(\AA) \smallskip      \\ \hline 
J033225.26-      & 03:32:25.26 & -27:45:23.9 & 0.6660 & $9.1_{-3.7}^{+1.3}$& $9.86_{-0.04}^{+0.05}$ & $7.00\pm 0.51$\\ 
274524.0     & &  &  &         \\
J033231.36-      & 03:32:31.35 & -27:47:24.9 &   0.6669 & $10.5_{-1.6}^{+1.7}$ & $10.02_{-0.03}^{+0.03}$&$6.50 \pm 0.51$\\
274725.0      & &  &   &        \\
J033230.03-      & 03:32:30.03 & -27:43:47.2  &   0.6679 & $3.8_{-0}^{+0}$ & $10.98_{-0.0}^{+0.01}$ &$6.44 \pm 0.51$\\
274347.3      & &  &   &        \\
J033229.64-      & 03:32:29.64 & -27:42:42.5 & 0.6671 & $40.5_{-12.1}^{+8.2}$ & $10.30_{-0.03}^{+0.07}$ &$6.70 \pm 0.51$\\
274242.6     & &  &     &      \\
J033230.57-      & 03:32:30.56 & -27:45:18.2 &   0.6807  & $12.6_{-2.1}^{+1.7}$ & $10.48_{-0.07}^{+0.03}$ &$5.60 \pm 0.52$ \\
274518.2      & &  &  &         \\ \hline 
\end{tabular}

@@

\begin{figure*}[ht!]
\centering
\includegraphics[scale=.61]{HEII_final.png}
\includegraphics[scale=.61]{HEII3000_final.png}
\caption{Top: HeII+47 image after stacking. Bottom: HeII3000+48 image after stacking. }
\label{fig:stacked_image}
\end{figure*}
\section{Analysis}

@@

\subsection{Limits on the MgII emission}
The surface brightness profiles presented in Fig. \ref{fig:sb_profiles} do not exhibit any signs of extended MgII emission. Previous constraints on the brightness of any possible emission are given by  \citep{Rubin_2011}. In this work the authors studied emission in a starburst galaxy at $z=0.69$ with a star formation rate of 80 $M_{\odot} yr^{-1}$. In a two-dimensional Keck/LRIS spectrum of this galaxy, they measured fluxes of $4.04 \pm 0.4$ to $8.0\pm 0.4$ $10^{-18}$ergs sec $^{-1}$ cm$^{-2}$  above and below the continuum region of the 2D spectra at $\lambda 2796$. Converting the 3$\sigma$ detection limit of our continuum-subtracted MgII image into flux units, we report the MgII emission 3$\sigma$ limits as 5.37 $10^{-18}$ergs sec $^{-1}$ cm$^{-2}$. Comparing our SB limit to previously reported values, it should be possible to detect the emission of this galaxy.

\subsection{MgII absorption in the line-profile}
Although we do not measure any extended MgII emission, we do observe a decrement of flux in the galaxy continua measured in the MgII filter in 3 galaxies out of the 5 galaxy sample. In the following section we discuss the absorption in each of these three galaxies, as well as our null detections.

We first discuss the case of a null detection of MgII absorption. The galaxy J033230.57 at a redshift of $z=0.6807$ is the most redshifted galaxy of the sample. This galaxy shows no significant flux decrement in the MgII filter. Examining Figure \ref{fig:case_images}, we can see that there should not be any absorption measured in J033230.57, as the absorption profile in the spectrum appears both in the HeII and HeII/3000 filter. This is a good test of our flux calibration, as it appears that there are no hints of systematic false absorption signatures.

@@

The next galaxy that shows an decrement of flux from MgII absorption is J033231.36. The MgII absorption spills outside the $1\sigma$ continuum flux contour, however a significant amount lies within our $1\sigma$ significant detection. The mean value of the EW of this galaxy is $6.91 \pm 0.560$ \AA, and is in good agreement with the EW calculated from the Keck/LRIS spectra, $6.50 \pm 0.51$ \AA. Again, inspection of the distribution of the EW over the pixels, reveal a possible outlier of an $EW\approx 20$\ \AA.

\begin{figure*}
\centering
\gridline{\fig{J033225_26.pdf}{0.5\textwidth}{(J033225.26)}
          \fig{J033230_03.pdf}{0.5\textwidth}{(J033230.03)}}
\gridline{\fig{J033230_64.pdf}{0.5\textwidth}{(J033230.64)}
          \fig{J033231_36.pdf}{0.5\textwidth}{(J033231.36)}}
\caption{Surface brightness profiles for galaxies that exhibit flux decrements from MgII absorption. Photometry was performed with circular apertures with increasing inner and outer radii. The error bars are determined from a SWarp RMS map .}
\label{fig:sb_profiles}
\end{figure*}

\begin{figure*}[!htb]
\centering
\includegraphics[scale=0.7]{stamps.pdf}
\caption{ $10'' \times 10''$ images stamps. Bottom: Continuum flux in ergs/s/cm$^2$/arcsec. Top: Continuum subtracted MgII flux, absorption can be seen in 3 of 5 galaxies. Each stamp is scaled with symmetric limits around 0.}
\label{fig:stamp_images}
\end{figure*}

\begin{figure*}[!htb]
\centering
\includegraphics[scale=0.58]{filt_57_spectra.pdf}
\includegraphics[scale=0.58]{filt_64_spectra.pdf}
\includegraphics[scale=0.58]{filt_03_spectra.pdf}
\includegraphics[scale=0.58]{filt_26_spectra.pdf}
\includegraphics[scale=0.58]{filt_36_spectra.pdf}
\caption{KECK/LRIS spectra plotted with the transmission curves of the filters HeII+47 and HeII/3000+48. The MgII doublet falls fortuitously the central wavelength of the HEII+47 filter. }
\label{fig:spec_images}
\end{figure*}

\begin{figure*}[ht!]
\centering
\includegraphics[scale=.58]{J03EW.pdf}
\includegraphics[scale=.58]{J64EW.pdf}
\includegraphics[scale=.58]{J26EW.pdf}
\includegraphics[scale=.58]{J57EW.pdf}
\includegraphics[scale=.58]{J36EW.pdf}
\caption{ Plots of the distribution of equivalent widths inside a $1\sigma$ continuum flux outline. }
\label{fig:ew_images}
\end{figure*}

\section{Analysis}
\section{Conclusion}
We presented the results of a narrowband imaging search for MgII emission in a sample of GOODS-S galaxies at a redshift of $z \approx 0.70$. Although we were unable to detect any measurable amount of MgII emission, We were able to detect a non-trivial amount of MgII absorption in 3 of our 5 galaxy sample. Our images, which are effective in creating absorption maps, were used to calculate the EW of absorption inside a $1\sigma$ continuum contour. 
\bibliography{references2017}

>>>>

\begin{document}
\title{A VLT/FORS2 Narrowband Imaging Search for \ion{Mg}{2} Emission Around $\lowercase{z}\sim0.7$ Galaxies }
\author{Ryan Rickards Vaught \altaffilmark{1}, Kate H. R. Rubin \altaffilmark{1}, Fabrizio Arrigoni Battaia \altaffilmark{2},  Joseph Hennawi, J. Xavier Prochaska}

@@

\begin{abstract}
Galactic-scale outflows are thought to be the primary mechanism in the removal of cool gas in star-forming galaxies. 
%
Presently, the mass and energy of these flows remain poorly constrained.
%
One way to better constrain these parameters is to measure the spatial extent of the outflow; however, measuring the spatial extent of such outflows via spectral methods has been traditionally very difficult due to the faintness of emission lines tracing outflowing material. 
%
We present VLT/FORS2 narrowband imaging of 5 star forming galaxies at redshift $z=0.67-0.69$ in the GOODS-S field as part of an effort to spatially resolve large-scale outflows traced by \ion{Mg}{2} emission. 
%
Previous spectra of this sample have already revealed winds traced by \ion{Mg}{2} absorption. 
%
At our sample redshift, the \ion{Mg}{2} emission lines fall exactly within the FORS2 HeII+47 and HeII/3000+48 interference filters.
%
The total integration time of 10 hrs obtained in each filter permits the analysis of the flow surface brightness and extent on scales over which \ion{Mg}{2} is typically detected in absorption (i.e., projected distances $> 100$ kpc). 
%
Such measurements can provide stronger constraints on the mass and energy of feedback, helping to advance our understanding of the processes regulating galaxy evolution up to $z=1$. 
\end{abstract}

@@

\section{Introduction}
Galactic scale outflows are considered to be a main driver of galaxy evolution, as they provide a means to transport cool gas away from star forming regions out to the intergalactic medium. 
%
%
In other words, this removal of cool gas carries away the necessary fuel that is required for stellar formation. 
%
%
Even though outflows play a critical role in the star formation rates and mass of the host galaxy \citep{Werk_2014}, the physical production mechanism that powers these outflows remains uncertain.
%
%
Despite the uncertainty, some possible mechanics have been proposed by theoretical studies that include thermal pressure from core collapse supernova, radiation pressure from starbursts and finally cosmic ray pressure \citep{Sugahara_2017,Larson_1974,Chevalier_1985,Springel_2003}. 
%
%
An accurate picture of what types of galaxies host outflows comes from numerous spectroscopic studies(authors), as outflows are detected by measuring the blueshift of absorption transitions with respect to the host galaxy systematic velocities.
%
%
Spectroscopy of galaxies from low to high redshifts and over a wide range of star formation rates have revealed outflows in galaxies which host large concentrations of massive stars (e.g., \cite{Rubin_2014} Martin 2012). 
%

% New Paragraph
One common practice in detecting the presence of gas in distant galaxies has been to spectroscopically probe galactic halos along background quasar sight lines and down-the-barrel observations.
%
With temperatures of the cool halo gas component on the order of $10^4\ K$, the gas can be traced by the absorption of metals such \ion{Mg}{2}, Fe and others \citep{Bordoloi_2011, Bergeron_1986}. 
%
Nonetheless, this method is weak in constraining the overall radial profile, extent and morphology of the outflow. 
%
It follows from these weak constraints that estimates of mass and energy loss are left uncertain by at least two order of magnitude \citep{Rubin_2014}.

%%%% KHRR
\begin{itemize}
\item One novel way of developing these constraints is to trace the extent of winds in emission

\item This has been done in the optical (in H$\alpha$, [\ion{O}{3}]) for nearby starbursts -- these transitions trace a warm, shock-heated phase

\item In a study by \cite{Rubin_2011} strong \ion{Mg}{2} emission with a P-Cygni line profile was observed in the GOODS-N galaxy TKRS 4389. A proposed production mechanism for the observed \ion{Mg}{2} emission is photon scattering.

\item This latter mechanism makes it possible to study winds in emission beyond the local universe

\item Summary of experiment: in this paper, we present the first narrowband imaging of \ion{Mg}{2} line emission in a sample of five distant ($z\sim0.7$) star-forming galaxies.  State the measurement we're making (SB limit, 2D absorption morphology).

\item Roadmap of paper sections for the reader.

\end{itemize}
%%%% end KHRR

\section{Observations and Data Reduction}

%%%% KHRR
\subsection{Sample Selection}

Our target galaxies were selected from a Keck/LRIS survey of UV absorption lines in $\approx 100$ objects having redshifts $0.3< z < 1.4$ and $B_{AB}< 23$ in fields with deep \emph{HST}/ACS imaging \citep{Rubin_2014}.  In particular, this parent survey targeted galaxies in a total of nine Keck/LRIS pointings located in both of the GOODS fields \citep{Giavalisco2004} and the AEGIS survey field (the Extended Groth Strip; \cite{Davis2007}).  In inspecting the redshift distribution of this sample,

Figure~\ref{fig.hstims}
%%%%

%
The  sample is fortuitously distributed on the sky such that it can be imaged in a single FORS2 pointing.

\subsection{VLT/FORS2 Observations}
% New Paragraph
The data were taken in service-mode using the FORS2 instrument on the VLT 8.2m telescope Antu between October 2012 and February 2013. 
%
We used two narrowband filters, HeII+47 and HeII/3000+48, that have peak transmission at wavelengths that correspond to the \ion{Mg}{2} doublet lines at our sample redshift of $z\approx 0.7$ (see Table \ref{tab:filters}).
%
The FORS2 has a pixel scale of $0.25''$ pixel$^{-1}$ and a field of view of $7'\times7'$.
%
Summing the individual exposure times for each image results in a combined exposure time of $10.0$ hours each for the HeII+47 and HeII/3000+48 filters.
%
We carried out our observations under photometric and thin cloud conditions (program ID: 090.A-0427A).

\begin{figure*}[!ht]
\centering
\includegraphics[scale=.75,trim=50 100 100 350,clip=]{../Figures/fors2_color_imstamps.pdf}
\caption{Color imaging of our sample galaxies in the \emph{HST}/ACS F435W, F606W, and F775W filters obtained as part of the GOODS survey \citep{Giavalisco2004}.
%From Top Left to Right Bottom: J033230.03, J033230.64, J033225.26, J033231.36, J033230.57.
Each image is $5\arcsec\times5\arcsec$.
%%% Reminder to KHRR: made with ~/Research/MgII/paper_mgii/Paper2/Analysis/figpro/vaught2017_make_justcolorims.pro
\label{fig.hstims}}
\end{figure*}

\begin{figure}[h]
\centering
\includegraphics[scale=.55]{../Figures/avg_seeing_HEII.pdf}
\includegraphics[scale=.55]{../Figures/avg_seeing_HEII3000.pdf}
\caption{  Distribution of seeing conditions for individual exposures comprising our dataset.
\textbf{Top}: for the HeII+47 images. The median seeing is $1.03\arcsec$ 
\textbf{Bottom}: Same for the HEII/3000+48 images. The median seeing is $1.08\arcsec$. 
The seeing conditions were calculated by ESO and were provided in the header of each science image.}
\end{figure}

The data were reduced using custom routines written in \textbf{Python}. 
%%
The images were first corrected by subtracting and removing the overscan region of the CCD. 
%%
Then the images were bias-subtracted and flat-fielded using twilight flats. 
%%
Each individual image was cleaned of cosmic rays and bad pixels by utilizing the L.A Cosmic algorithm.
%%
 The astrometry solutions were calculated via Astrometry.net \citep{Lang} with a standard deviation in the galaxy coordinates of $\sigma \approx 0.10''$. 
%%
Before image stacking, we ran each frame through \textbf{SExtractor} \citep{Bertin} in order to create a Root-Mean-Square map of each science image.
%%
 These frames, in addition to the science images, are stacked to create a co-added RMS image.
%% New Paragraph
The final stacked images for each filter is obtained using \textbf{SWarp} \citep{Bertin}.
%%
Each individual frame is first sky-subtracted using a background mesh size of 256 pixels which is approximately $64''$. 
%%
We chose the mesh size to be large enough such that the extended emission is not mistakenly subtracted \citep{Battaia_2015}. 
%%
The frame, after background-subtraction, is resampled onto a common astrometric solution using a \textit{Lancosz3} interpolation kernel. 
%%
The images are median-combined in order to increase the signal to noise of any \ion{Mg}{2} emission. \textbf{SWarp} is also configured to produce RMS weight map from our \textbf{SExtractor} weighted images.

Once image stacking was done, we were left with two images to perform photometry on. One image contains only continuum photons, while the other one contains continuum + \ion{Mg}{2} photons.  (see Figure \ref{fig:stacked_image}). One side effect from stacking is that the east and west borders of each image contain greater noise compared to the center of the image. This is due to the imperfect overlap of the 3 pointings used. However, the sample galaxies are sufficiently distant from these low S/N regions that their photometry is not affected. As a final step, both images are aligned in physical coordinates via the IRAF \textbf{Imalign} command \citep{Tody_1986}.

@@

\begin{table*}[t]
\centering
\caption{Properties of 5 galaxies in our sample :  These properties were taken from \cite{Rubin_2014}. All galaxies are at roughly the same redshift. The star formation rates for the sample range from 3.8 to 40.5 solar mass per year. The EW are for the blended components of the \ion{Mg}{2} doublet and were calculated with Eq. \ref{eq:specEW} and the supplemental Keck/LRIS spectra}
\begin{tabular}{lllllll} \hline \hline
Object & R.A. & Dec  & $z$ & SFR($M_{\odot} yr^{-1}$) & $\log{M_{*}/M_{\odot}}$ & EW(\AA) \smallskip      \\ \hline 
J033225.26-      & 03:32:25.26 & -27:45:23.9 & 0.6660 & $9.1_{-3.7}^{+1.3}$& $9.86_{-0.04}^{+0.05}$ & $7.00\pm 0.51$\\ 
274524.0     & &  &  &         \\
J033231.36-      & 03:32:31.35 & -27:47:24.9 &   0.6669 & $10.5_{-1.6}^{+1.7}$ & $10.02_{-0.03}^{+0.03}$&$6.50 \pm 0.51$\\
274725.0      & &  &   &        \\
J033230.03-      & 03:32:30.03 & -27:43:47.2  &   0.6679 & $3.8_{-0}^{+0}$ & $10.98_{-0.0}^{+0.01}$ &$6.44 \pm 0.51$\\
274347.3      & &  &   &        \\
J033229.64-      & 03:32:29.64 & -27:42:42.5 & 0.6671 & $40.5_{-12.1}^{+8.2}$ & $10.30_{-0.03}^{+0.07}$ &$6.70 \pm 0.51$\\
274242.6     & &  &     &      \\
J033230.57-      & 03:32:30.56 & -27:45:18.2 &   0.6807  & $12.6_{-2.1}^{+1.7}$ & $10.48_{-0.07}^{+0.03}$ &$5.60 \pm 0.52$ \\
274518.2      & &  &  &         \\ \hline 
\end{tabular}

@@

\begin{figure*}[ht!]
\centering
\includegraphics[scale=.61]{../Figures/HEII_final.png}
\includegraphics[scale=.61]{../Figures/HEII3000_final.png}
\caption{Top: HeII+47 image after stacking. Bottom: HeII3000+48 image after stacking. }
\label{fig:stacked_image}
\end{figure*}
\section{Analysis}

@@

\subsection{Limits on the \ion{Mg}{2} emission}
The surface brightness profiles presented in Fig. \ref{fig:sb_profiles} do not exhibit any signs of extended \ion{Mg}{2} emission. Previous constraints on the brightness of any possible emission are given by  \citep{Rubin_2011}. In this work the authors studied emission in a starburst galaxy at $z=0.69$ with a star formation rate of 80 $M_{\odot} yr^{-1}$. In a two-dimensional Keck/LRIS spectrum of this galaxy, they measured fluxes of $4.04 \pm 0.4$ to $8.0\pm 0.4$ $10^{-18}$ergs sec $^{-1}$ cm$^{-2}$  above and below the continuum region of the 2D spectra at $\lambda 2796$. Converting the 3$\sigma$ detection limit of our continuum-subtracted \ion{Mg}{2} image into flux units, we report the \ion{Mg}{2} emission 3$\sigma$ limits as 5.37 $10^{-18}$ergs sec $^{-1}$ cm$^{-2}$. Comparing our SB limit to previously reported values, it should be possible to detect the emission of this galaxy.

\subsection{\ion{Mg}{2} absorption in the line-profile}
Although we do not measure any extended \ion{Mg}{2} emission, we do observe a decrement of flux in the galaxy continua measured in the \ion{Mg}{2} filter in 3 galaxies out of the 5 galaxy sample. In the following section we discuss the absorption in each of these three galaxies, as well as our null detections.

We first discuss the case of a null detection of \ion{Mg}{2} absorption. The galaxy J033230.57 at a redshift of $z=0.6807$ is the most redshifted galaxy of the sample. This galaxy shows no significant flux decrement in the \ion{Mg}{2} filter. Examining Figure \ref{fig:case_images}, we can see that there should not be any absorption measured in J033230.57, as the absorption profile in the spectrum appears both in the HeII and HeII/3000 filter. This is a good test of our flux calibration, as it appears that there are no hints of systematic false absorption signatures.

@@

The next galaxy that shows an decrement of flux from \ion{Mg}{2} absorption is J033231.36. The \ion{Mg}{2} absorption spills outside the $1\sigma$ continuum flux contour, however a significant amount lies within our $1\sigma$ significant detection. The mean value of the EW of this galaxy is $6.91 \pm 0.560$ \AA, and is in good agreement with the EW calculated from the Keck/LRIS spectra, $6.50 \pm 0.51$ \AA. Again, inspection of the distribution of the EW over the pixels, reveal a possible outlier of an $EW\approx 20$\ \AA.

\begin{figure*}
\centering
\gridline{\fig{../Figures/J033225_26.pdf}{0.5\textwidth}{(J033225.26)}
          \fig{../Figures/J033230_03.pdf}{0.5\textwidth}{(J033230.03)}}
\gridline{\fig{../Figures/J033230_64.pdf}{0.5\textwidth}{(J033230.64)}
          \fig{../Figures/J033231_36.pdf}{0.5\textwidth}{(J033231.36)}}
\caption{Surface brightness profiles for galaxies that exhibit flux decrements from \ion{Mg}{2} absorption. Photometry was performed with circular apertures with increasing inner and outer radii. The error bars are determined from a SWarp RMS map .}
\label{fig:sb_profiles}
\end{figure*}

\begin{figure*}[!htb]
\centering
\includegraphics[scale=0.7]{../Figures/stamps.pdf}
\caption{ $10'' \times 10''$ images stamps. Bottom: Continuum flux in ergs/s/cm$^2$/arcsec. Top: Continuum subtracted \ion{Mg}{2} flux, absorption can be seen in 3 of 5 galaxies. Each stamp is scaled with symmetric limits around 0.}
\label{fig:stamp_images}
\end{figure*}

\begin{figure*}[!htb]
\centering
\includegraphics[scale=0.58]{../Figures/filt_57_spectra.pdf}
\includegraphics[scale=0.58]{../Figures/filt_64_spectra.pdf}
\includegraphics[scale=0.58]{../Figures/filt_03_spectra.pdf}
\includegraphics[scale=0.58]{../Figures/filt_26_spectra.pdf}
\includegraphics[scale=0.58]{../Figures/filt_36_spectra.pdf}
\caption{KECK/LRIS spectra plotted with the transmission curves of the filters HeII+47 and HeII/3000+48. The \ion{Mg}{2} doublet falls fortuitously the central wavelength of the HEII+47 filter. }
\label{fig:spec_images}
\end{figure*}

\begin{figure*}[ht!]
\centering
\includegraphics[scale=.58]{../Figures/J03EW.pdf}
\includegraphics[scale=.58]{../Figures/J64EW.pdf}
\includegraphics[scale=.58]{../Figures/J26EW.pdf}
\includegraphics[scale=.58]{../Figures/J57EW.pdf}
\includegraphics[scale=.58]{../Figures/J36EW.pdf}
\caption{ Plots of the distribution of equivalent widths inside a $1\sigma$ continuum flux outline. }
\label{fig:ew_images}
\end{figure*}

\section{Analysis}
\section{Conclusion}
We presented the results of a narrowband imaging search for \ion{Mg}{2} emission in a sample of GOODS-S galaxies at a redshift of $z \approx 0.70$. Although we were unable to detect any measurable amount of \ion{Mg}{2} emission, We were able to detect a non-trivial amount of \ion{Mg}{2} absorption in 3 of our 5 galaxy sample. Our images, which are effective in creating absorption maps, were used to calculate the EW of absorption inside a $1\sigma$ continuum contour. 
\bibliography{references2017}
